Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-15 03_Prep_data.Rmd
Add disease risk factor

>>>>

****

### Disease presure factor
We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure. We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot. 
We will create two categories, `lowD` and `highD`. 
We will use the median `AUDPC` to separate the trials into these two groups.

```{r}

slimmer_PM_dat$D_pres <- NA_character_

Trial_Dpress <- slimmer_PM_dat %>%
   group_by(trial_ref) %>%
   filter(fungicide_ai == "control") %>%
   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))

median_AUDPC <- median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)

sort(Trial_Dpress$AUDPC_C)

for(i in unique(slimmer_PM_dat$trial_ref)) {
   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
      next()
   }

   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
   {
      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
   } else{
      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
      } else{
         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
            NA_character_
      }

   }
}

Lets have a quick look to examine weather trials with high disease pressure sustain a greater yield loss.

```{r}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()
```

From this plot we see that in the trials with high disease pressure treatments on tended to produce lower yields. 
There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
